### 2020-08-22 paper/definitions.tex
More defs wip

\begin{defn}[subgraph]
  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if $V' \subset V$ and $E' \subset E$.
\end{defn}

\begin{defn}[induced subgraph]
  If $G' = (V', E')$ is a subgraph of $G$ and it contains \emph{all edges} of $G$ that join two vertices in $V'$, then $G'$ is said to be \emph{induced subgraph} of $G$ and is denoted $G[V']$.
\end{defn}
For example $(\{v_1, v_2, v_3\}, \{v_1v_2\})$ is \emph{not} an induced subgraph of the example graph $G_0$, while $(\{v_1, v_2, v_3\}, \{v_1v_2, v_2v_3\}) = G_0[\{v_1, v_2, v_3\}]$ is.

@@

@@

If a path or a cycle has an odd length, it will be called \emph{odd}. Otherwise, it will be called \emph{even}.

@@

@@

@@

Therefore an \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets}. In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subset V$ will be called \emph{independent} (in the context of $G$) iff $G[V']$ is an anticlique.

@@

% \begin{defn}[independent set]
  % An \emph{independent set} or 
% \end{defn}

>>>>

\begin{defn}[subgraph]
  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if $V' \subseteq V$ and $E' \subseteq E$.
\end{defn}

\begin{defn}[induced subgraph]
  If $G' = (V', E')$ is a subgraph of $G$ and it contains \emph{all edges} of $G$ that join two vertices in $V'$, then $G'$ is said to be \emph{induced subgraph} of $G$ and is denoted $G[V']$.
\end{defn}

Given a graph $G = (V, E)$ and a set set $X \subseteq V$ by $G\setminus X$ we will denote a induced subgraph $G[V\setminus X]$.

For example $(\{v_1, v_2, v_3\}, \{v_1v_2\})$ is \emph{not} an induced subgraph of the example graph $G_0$, while $(\{v_1, v_2, v_3\}, \{v_1v_2, v_2v_3\}) = G_0[\{v_1, v_2, v_3\}] = G_0 \setminus \{v_0\}$ is.

\begin{defn}[$X$-completeness]
  Given set $X \subseteq V$, vertex $v \notin X$ is \emph{$X$-complete} if it is adjacent to every node $x \in X$. A set $Y \subseteq V$ is $X$-complete if $X \cap Y = \emptyset$ and every node $y \in Y$ is $X$-complete.
\end{defn}

@@

\begin{defn}[connected graph]
  A graph $G$ is \emph{connected} if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$. \todo{formal enough?}
\end{defn}

\begin{defn}[component]
  A \emph{component} of a graph $G$ is its maximal connected induced subgraph.
\end{defn}

@@

@@

\begin{defn}[hole]
  A \emph{hole} is a cycle of length at least four.
\end{defn}

If a path, a cycle or a hole has an odd length, it will be called \emph{odd}. Otherwise, it will be called \emph{even}.

@@

\begin{defn}[anticomponent]
  An \emph{anticomponent} of a graph $G$ is an induced subgraph whose complement is a component in $G$.
\end{defn}

@@

Therefore an \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets}. In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) iff $G[V']$ is an anticlique.

@@

\begin{defn}[Berge graph]
  A graph $G$ is \emph{Berge} if both $G$ and $\overline{G}$ have no odd hole.
\end{defn}

\begin{defn}[perfect graph]
  A graph $G$ is \emph{perfect} if for its every induced subgraph $G'$ we have $\chi(G') = \omega(G')$
\end{defn}

\begin{defn}[C-major vertices]
  Given a shortest off hole $C$ in $G$, a node $v \in V(G) \setminus V(C)$ is $C-major$ if the set of its neighbors in $C$ is not contained in any 3-node path of $C$.
  \TODO{a picture of this, clean odd hole, amenable hole}
\end{defn}

\begin{defn}[clean odd hole]
  An odd hole $C$ of $G$ is \emph{clean} if no vertex in $G$ is $C$-major.
\end{defn}

\begin{defn}[cleaner]
  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{cleaner for $C$} if $X \cap V(C) = \emptyset$ and every $C$-major vertex belongs to $X$.
\end{defn}

Let us notice, that if $X$ is a cleaner for $C$ then $C$ is a clean hole in $G \setminus X$.

\begin{defn}[near-cleaner]
  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if $X$ contains all $C$-major vectices and $X \cap V(C)$ is a subset of vertex set of some 3-node path of $C$.
\end{defn}

\begin{defn}[amenable odd hole]
  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest off hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vectices there is a $X$-complete edge in $C$.
\end{defn}

### 2020-08-22 paper/main.tex
Defs WIP
Defs defs defs
More defs wip

\usepackage{appendix}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{intcalc}
\usepackage{amsthm}
\usepackage{cleveref}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

@@

\tableofcontents

@@

\section{Perfect Graphs}
All graphs in this paper are finite, undirected and have no loops or parallel edges. We denote the chromatic number of graph $G$ by $\chi(G)$ and the cardinality of the largest clique of $G$ by $\omega(G)$. \emph{Coloring} of a graph means assigning every node of a graph a color. A coloring is \emph{valid} iff every two nodes sharing an edge have different colors. An \emph{optimal} coloring (if exists) is a valid coloring using only $\omega(G)$ colors.

@@

\begin{wrapfigure}[14]{r}{0.35\textwidth}
	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
	\node(a) at (0,0) {a};
	\node(b1) at (-2,-6) {$b_1$};
	\node(b2) at (0,-4.268) {$b_2$};
	\node(b3) at (2,-6) {$b_3$};

@@

	\draw (a) to (b2);
\end{tikzpicture}
\caption{An example of a pyramid.}
\end{wrapfigure}

@@

	\tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
                       post length=0mm,pre length=0mm}}
	\draw[decorate] (p2) to [out=-100, in=180] (0, -5) to [out=0, in=-80] (p5);
	\node[draw=none] at (0, -4.7) {$P$};
\end{tikzpicture}
\caption{An example of a jewel.}
\end{wrapfigure}

@@

		% \draw (a) to (b2);
\end{tikzpicture}
\caption{An example of a $\T_2$.}
\end{wrapfigure}

>>>>

\usepackage{appendix}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{intcalc}
\usepackage{amsthm, amsfonts, thmtools}
\usepackage{cleveref}
\usepackage{floatflt}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{defn}{Definition}[section]
\renewcommand{\listtheoremname}{List of definitions}

@@

\listoftheorems[ignoreall,show={defn}]
\tableofcontents

@@

\section{Definitions}
\input{definitions.tex}

\section{Perfect Graphs}

All graphs in this paper are finite, undirected and have no loops or parallel edges. We denote the chromatic number of graph $G$ by $\chi(G)$ and the cardinality of the largest clique of $G$ by $\omega(G)$. \emph{Coloring} of a graph means assigning every node\todo{node \rightarrow vertex everywhere (seems to be more common name)} of a graph a color. A coloring is \emph{valid} iff every two nodes sharing an edge have different colors. An \emph{optimal} coloring (if exists) is a valid coloring using only $\omega(G)$ colors.

@@

% \begin{floatingfigure}{0.35\textwidth}

\begin{wrapfigure}{r}{0.35\textwidth}
	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
	\node(a) at (0,0) {a};
	\node(b1) at (-2,-6) {$b_1$};
	\node(b2) at (0,-4.268) {$b_2$};
	\node(b3) at (2,-6) {$b_3$};

@@

	\draw (a) to (b2);
\end{tikzpicture}%
\caption{An example  of a pyramid.}%
\vspace{-1.2cm}
% \end{floatingfigure}
\end{wrapfigure}

@@

	\tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
                       post length=0mm,pre length=0mm}}
	\draw[decorate] (p2) to [out=-100, in=180] (0, -5) to [out=0, in=-80] (p5);
	\node[draw=none] at (0, -4.7) {$P$};
\end{tikzpicture}
\caption{An example of a jewel.}
\vspace{-1.5cm}
\end{wrapfigure}

@@

		% \draw (a) to (b2);
\end{tikzpicture}%
\caption{An example of a $\T_2$.}%
\vspace{-1.5cm}
\end{wrapfigure}
